---
title: "R Markdown Implicit system views"
author: "Christa Blokhuis"
date: "2023-08-10"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Some details about the study and this document.

During eight interviews with experts in the field of protein transition, participants were asked to draw a causal loop diagram (CLD) based on a provided set of variables. By doing so, we would gain more insight in the diversity of approaches to consumption practices of protein sources and get a general idea of which variables are considered important in explaining consumption. Participants were asked to elicit their choices. In this R Markdown document, some explorative analysis of the interview transcripts and labelling is performed. 

## R Markdown

```{r count_dependent_variables, echo = FALSE, warning=FALSE, message=FALSE}
## -- set up

#load packages
library(tidyverse)
library(janitor)
library(viridis)
library(visNetwork)

#load data
myFile <- "..." #fill out file location of "labels_coding.csv"

data_labels <- read_delim(file = myFile,
                                delim = ";", 
                                col_names = TRUE)

myPalette <- c("lightpink", "lightgreen", "lightgrey", "lightskyblue", "lavender", "lightyellow", "lightsalmon", "darkgrey" )

participant_sequence <- c("one", "two", "three","four","five","six","eight","nine")
DONE_levels_sequence <- c("environment", "interpersonal", "individual", "policy", "demographics", "new", "behaviour")


data_labels <- clean_names(data_labels)
data_labels$deductive_coding_systems_thinking <- sapply(data_labels$deductive_coding_systems_thinking,
                                    function(x) { gsub("[\r\n]", "", x) })
data_labels$variables_mentioned_by_expert <- sapply(data_labels$variables_mentioned_by_expert,
                                    function(x) { gsub("[\r\n]", "", x) })




#show head of data
head(data_labels)
nrow(data_labels)
```

### Count variables mentioned by experts in their narrative

```{r count_variable_use, echo = FALSE, warning=FALSE, message=FALSE}

#split column containing variables into separate columns

data_vars_split <- data_labels %>%
  separate(col = variables_mentioned_by_expert, 
           c("var1","var2","var3","var4","var5","var6","var7","var8"),
           sep = ", ",
           fill = "right")



#pivot the three columns with labels to create one column of variables per participant

data_vars_pivot <- data_vars_split %>%
  pivot_longer(cols = c("var1","var2","var3","var4","var5","var6","var7","var8"),
               names_to = "var_names",
               values_to = "variables")

#clean up unnessecary rows and column
data_vars_clean <- data_vars_pivot[,-c(3,4)]
data_vars_clean <- data_vars_clean %>%
  filter(!is.na(variables))

#count number of variables per participant

data_vars_count <- data_vars_clean %>%
  group_by(variables, participant) %>%
  summarize(count_vars = n())

#set order of participants for legend of plot

data_vars_count$participant <- factor(data_vars_count$participant,
                                      levels = participant_sequence)

#since too many variables, group them per DONE scale level
myFile <- "..." # fill out file location of "vars_groups.csv" 

vars_groups <- read_csv(file = myFile, 
                        col_names = TRUE)
colnames(vars_groups)[1] <- "variables"


#add group name to each variable
data_vars_count_groups <- left_join(data_vars_count, vars_groups, 
                                    by = c("variables"))

#plot label count in histogram per participant

ggplot(data_vars_count_groups, 
       aes(x = variables, y = count_vars, fill = participant)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = count_vars), 
            size = 2,
            position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = myPalette) +
  theme_bw() +
  coord_flip() +
  labs(title = "Frequency of variables mentioned in interview per participant",
       x = "Variables", 
       y = "Number of variables used", 
       fill = "Participants") +
  theme(axis.text.y = element_text(size = 8))

# ======

#if necessary, complete columns of group names manually; otherwise, skip to after ======

setwd("...") # set your working directory to export the below file

#export and add group names that turned NA by hand
write.csv(data_vars_count_groups, file = "data_vars_count_groups.csv", sep = ";")


#import the file with complete column of group names

myFile <- "..." # fill out file location of "data_vars_count_groups_final.csv" 

data_vars_count_groups_final <- read_delim(file = myFile,
                                delim = ";", 
                                col_names = TRUE)
                                    
#plot DONE levels per participant mentioned in interview

#create data frame with count per DONE scale level

data_groups_count <- data_vars_count_groups_final %>%
  group_by(group, participant) %>%
  summarize(count_groups = n())

#create color table for groups:

myPalette_groups <- c("lightpink", "lightgreen", "lightgrey", "lightskyblue", "lavender", "lightyellow", "lightsalmon")

color_table <- tibble(
  color = myPalette_groups,
  group = DONE_levels_sequence
)

#set order of groups for legend of plot

data_groups_count$group <- factor(data_groups_count$group,
                                      levels = color_table$group)

ggplot(data_groups_count, aes(x = participant, y = count_groups, fill = group)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = count_groups), 
            size = 2,
            position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = color_table$color) +
  theme_bw() +
  labs(x = "Participants", y = "Number of variables mentioned", fill = "Scale level") +
  scale_x_discrete(limits = participant_sequence)

# ======


```
### Count deductive labels used to code narrative

```{r count_deductive_labels, echo = FALSE, warning=FALSE, message=FALSE}

#remove mistake labels
data_labels <- data_labels %>%
  filter(deductive_coding_systems_thinking != "Definition of variables",
         deductive_coding_systems_thinking != " ",
         deductive_coding_systems_thinking != "Definition of meat alternatives",
         deductive_coding_systems_thinking != "Relationships between variables;Relevancy of population")

#split column containing deductive labels into separate columns

data_labels_split <- data_labels %>%
  separate(col = deductive_coding_systems_thinking, 
           c("label1","label2","label3"),
           sep = ",",
           fill = "right")

#pivot the three columns with labels to create one column of labels per participant

data_labels_pivot <- data_labels_split %>%
  pivot_longer(cols = c("label1","label2","label3"),
               names_to = "labels",
               values_to = "deductive_label")

#clean up unnessecary rows and column
data_labels_clean <- data_labels_pivot[,-3]
data_labels_clean <- data_labels_clean %>%
  filter(!is.na(deductive_label))


#count number of data labels per participant

data_labels_count <- data_labels_clean %>%
  group_by(deductive_label, participant) %>%
  summarize(count_labels = n())

#set order of participants for legend of plot
data_labels_count$participant <- factor(data_labels_count$participant,
                                      levels = participant_sequence)

#plot label count in histogram per participant

ggplot(data_labels_count, 
       aes(x = deductive_label, y = count_labels, fill = participant)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = count_labels), 
            size = 2,
            position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = myPalette) +
  theme_bw() +
  theme(legend.title=element_text(size=10), 
    legend.text=element_text(size=8)) +
  coord_flip() +
  labs(x = "Labels", y = "Number of labels used", fill = "Participant") 

```